---
title: "Data-Driven Marketing: 1st Assignment"
author: "Group 3:Azzollini Francesca, Caramelli Leonardo, Mosezon Davide, Stefanelli Riccardo"
date: "2022-10-05"
output:
  html_document:
    
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)

```

```{r load_library, echo=FALSE}

library(readxl)
library(tidyverse) # the usual stuff: dplyr, readr, and other goodies
library(lubridate) # to handle dates
library(GGally) # for correlation-scatter plot matrix
library(ggfortify) # to produce residual diagnostic plots
library(rsample) # to split dataframe in training- & testing sets
library(janitor) # clean_names()
library(broom) # use broom:augment() to get tidy table with regression output, residuals, etc
library(huxtable) # to get summary table of all models produced
library(kableExtra) # for formatting tables
library(moderndive) # for getting regression tables
library(skimr) # for skim
library(mosaic)
library(leaflet) # for interactive HTML maps
library(tidytext)
library(viridis)
library(vroom)
library(kableExtra)
library(performance)
library(patchwork)


```

# Assignment_1

## Description

The database I am sharing with you is from a major European book retailer operating in one country. The retailer uses three sales channels---physical retail stores, catalogs, and the Internet---and uses a subscription business model. Thus, to be eligible to purchase, each customer must become a member. A code is associated with each customer, tracking each time they buy and from which channel. Therefore, we have information on which channel each customer selected on each purchase occasion, the date in which he/she was acquired and when he/she terminated the subscription, how much was spent, and age and gender demographics. Each channel shares the same assortment and price.

You can observe customers from January 2001 till June 2006. The dataset includes a cohort of customers acquired in 2001. Hereafter you will find a description of the variables included in the dataset.

I will ask you to explore this dataset. Extract the information it contains and relate it to decision problems.

I expect you to hand in a report on this analysis by Monday 10th, at 24:00.

## Analysys

```{r first_analysis, echo=FALSE}

df_assigment_1 <- read_excel("datichannel2022.xlsx")

glimpse(df_assigment_1)
skim(df_assigment_1)


```


```{r second_analysis}
#Active people
df_assigment_1_notActive <- df_assigment_1 %>% 
  filter(yearEND > 1)

df_assigment_1_Active <- df_assigment_1 %>% 
  filter(yearEND < 1)

```
## Not active customer
```{r notActiveCustomerAnalysis}
#Active customer
count(df_assigment_1_Active)

#Lost customer
count(df_assigment_1_notActive)

#Calculate how many days 
df_assigment_1_notActive <- df_assigment_1_notActive %>% 
  mutate(totalDays = date_END - date_BEGIN) %>% 
  filter(!is.na(totalDays))

#Calculate the median
df_assigment_1_notActive %>% 
  summarise(medianDuration = median(totalDays, na.rm = TRUE))

df_assigment_1_notActive %>% 
  filter(!is.na(totalDays)) %>% 
  ggplot(aes(totalDays)) + 
  geom_histogram(binwidth = 10) +
  labs(title = "Title", 
        subtitle = "SubTitle") +
  theme(plot.caption = element_text(hjust= 1), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank())

#How customer were catched
df_assigment_1_notActive %>% 
  summarise(countStreetAgent = count(StreetAgent),
            countDoorAgent = count(DoorAgent))
#Convert date to integer
df_assigment_1_notActive$totalDays <- as.numeric(as.character(df_assigment_1_notActive$totalDays))

df_assigment_1_notActive %>% 
  select(totalDays, revenues_total, Frequency_total, age, ret_year_total, qta_total) %>% 
  ggpairs(alpha = 0.3)

```

## Active Customer
```{r activeCustomer}

mean_city <- df_assigment_1 %>% 
  filter(mean_city == 1) %>% 
  select(vpccdpro) %>% 
  pull()


df_assigment_1_Active %>% 
  group_by(vpccdpro) %>% 
  summarise(countActive = count(vpccdpro)) %>% 
  mutate(meanCity = vpccdpro%in%mean_city) %>% 
  mutate(vpccdpro = fct_reorder(vpccdpro, countActive)) %>%
  ggplot(aes(x=vpccdpro,y=countActive,fill=meanCity)) +
  geom_col()


```

