---
title: "Data-Driven Marketing: 1st Assignment"
author: "Group 3:Azzollini Francesca, Caramelli Leonardo, Mosezon Davide, Stefanelli Riccardo"
date: "2022-10-05"
output:
  html_document:
    
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)

```

```{r load_library, echo=FALSE}

library(tidyverse)
library(skimr)
library(lubridate)
library(readxl)

```

# Assignment_1

## Description

The database I am sharing with you is from a major European book retailer operating in one country. The retailer uses three sales channels---physical retail stores, catalogs, and the Internet---and uses a subscription business model. Thus, to be eligible to purchase, each customer must become a member. A code is associated with each customer, tracking each time they buy and from which channel. Therefore, we have information on which channel each customer selected on each purchase occasion, the date in which he/she was acquired and when he/she terminated the subscription, how much was spent, and age and gender demographics. Each channel shares the same assortment and price.

You can observe customers from January 2001 till June 2006. The dataset includes a cohort of customers acquired in 2001. Hereafter you will find a description of the variables included in the dataset.

I will ask you to explore this dataset. Extract the information it contains and relate it to decision problems.

I expect you to hand in a report on this analysis by Monday 10th, at 24:00.

## Analysys

```{r first_analysis, echo=FALSE}

df_assigment_1 <- read_excel("datichannel2022.xlsx")

glimpse(df_assigment_1)
skim(df_assigment_1)


```
