---
title: "Artea_Analysis"
date: "2022-10-17"
author: "Group 3:Azzollini Francesca, Caramelli Leonardo, Mosezon Davide, Stefanelli Riccardo"
output:
  html_document:
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)

```

```{r}
library(knitr)
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = xfun::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

```{r load_library, echo=FALSE}

library(readxl)
library(tidyverse) # the usual stuff: dplyr, readr, and other goodies
library(lubridate) # to handle dates
library(GGally) # for correlation-scatter plot matrix
library(ggfortify) # to produce residual diagnostic plots
library(rsample) # to split dataframe in training- & testing sets
library(janitor) # clean_names()
library(broom) # use broom:augment() to get tidy table with regression output, residuals, etc
library(huxtable) # to get summary table of all models produced
library(kableExtra) # for formatting tables
library(moderndive) # for getting regression tables
library(skimr) # for skim
library(mosaic)
library(leaflet) # for interactive HTML maps
library(tidytext)
library(viridis)
library(vroom)
library(kableExtra)
library(performance)
library(patchwork)
library(car)
library(performance)
library(huxtable)
```

# Artea_Analysis

## First analysis

```{r load_file, echo=TRUE}

df_artea <- read_excel("data/Artea_main database.xlsx")

skim(df_artea)

```

```{r channel_analysis, echo=TRUE}

df_artea %>% 
  group_by(channel_acq, test_coupon) %>% 
  summarise(medianBrowsing = median(browsing_minutes),
            countValue = count(channel_acq),
            sumTrans_after = sum(trans_after)) %>% 
  ggplot(aes(x=channel_acq, y=countValue, fill=medianBrowsing)) +
  geom_col(stat = 'identity', position = 'dodge') + 
  theme_bw() +
  facet_wrap(vars(test_coupon), nrow=1)+
  labs(title = "Test coupon by channel acquisition")

df_artea %>% 
  group_by(channel_acq, test_coupon) %>% 
  summarise(medianBrowsing = median(browsing_minutes),
            countValue = count(channel_acq),
            sumTrans_after = sum(trans_after)) %>% 
  ggplot(aes(x=channel_acq, y=sumTrans_after, fill=medianBrowsing)) +
  geom_col(stat = 'identity', position = 'dodge') + 
  theme_bw() +
  facet_wrap(vars(test_coupon), nrow=1)

df_artea <- df_artea %>% 
  mutate(gross_rev_no20ptc = (revenue_after* 1.2 * test_coupon))  

df_artea %>% 
  group_by(channel_acq, test_coupon) %>% 
  summarise(medianBrowsing = median(browsing_minutes),
            countValue = count(channel_acq),
            sumRevenue_after = sum(revenue_after)) %>% 
  ggplot(aes(x=channel_acq, y=sumRevenue_after, fill=medianBrowsing)) +
  geom_col(stat = 'identity', position = 'dodge') + 
  theme_bw() +
  facet_wrap(vars(test_coupon), nrow=1)

```

## Was the test properly conducted?

```{r regres, echo=TRUE}

df_artea$channel_acq <- as.character(df_artea$channel_acq)

df_artea$channel_acq <- gsub("1", "Google", df_artea$channel_acq)
df_artea$channel_acq <- gsub("2", "Facebook", df_artea$channel_acq)
df_artea$channel_acq <- gsub("3", "Instagram", df_artea$channel_acq)
df_artea$channel_acq <- gsub("4", "Referral", df_artea$channel_acq)
df_artea$channel_acq <- gsub("5", "Other", df_artea$channel_acq)
  

df_artea_wider <- df_artea %>%
  pivot_wider(names_from = channel_acq,
              values_from = channel_acq,
              values_fill = "0") 

df_artea_wider$Google <- as.double(gsub("Google","1", df_artea_wider$Google))
df_artea_wider$Facebook <- as.double(gsub("Facebook","1", df_artea_wider$Facebook))
df_artea_wider$Instagram <- as.double(gsub("Instagram","1", df_artea_wider$Instagram))
df_artea_wider$Referral <- as.double(gsub("Referral","1", df_artea_wider$Referral))
df_artea_wider$Other <- as.double(gsub("Other", "1",df_artea_wider$Other))
  
  

#regressione logistica  --- per randomizzazione
model2 <-glm(test_coupon ~  Google + Facebook + Instagram + Referral + Other, data=df_artea_wider)
mosaic::msummary(model2)  


model2_1<-lm(test_coupon ~  Google + Facebook + Instagram + Referral + Other + num_past_purch + spent_last_purchase + weeks_since_visit + shopping_cart, data=df_artea_wider)
mosaic::msummary(model2_1) 


df_artea  %>%
  filter(test_coupon == 1) %>% 
  select(-c(id, test_coupon, channel_acq)) %>%  
  ggpairs(alpha = 0.3)

```

*According to model2_1 the randomization of customer is correct*

## What are your insights from the test? Did revenues increase? Did transactions?

```{r lcor2, echo=TRUE}

df_artea %>%
  group_by(test_coupon) %>%
  summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after))

```

*revenue più basso per 1, trans inverso*

## Is the effect of the test homogeneous? SI

```{r df, echo=TRUE}


df_artea_3 <- df_artea %>%
  group_by(test_coupon, shopping_cart, channel_acq) %>%
  summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after))
df_artea_3

var.test(revenue_after_tot ~ test_coupon, df_artea_3)
var.test(revenue_after_tot ~ shopping_cart, df_artea_3)
var.test(trans_after_tot ~ test_coupon, df_artea_3)
var.test(trans_after_tot ~ shopping_cart, df_artea_3)

```

*Every p-value (p = 0.8,1,0.3,0.9) which are greater than the significance level 0.05. In conclusion, there is no significant difference between the two variances.*

## Which of the new users should receive a coupon?

```{r df3, echo=TRUE}

df_artea_4 <- df_artea %>%
  filter(shopping_cart == 0, num_past_purch == 0) %>% 
  group_by(test_coupon, channel_acq) %>%
  summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after), id_count = sum(counts(id)))
df_artea_4

```

*google no, facebook top, ok instagram, no other che è diminuito e buono referral che ha avuto un incremento da 0 a 2, più o meno stesso numero di persone per channel*

## Would Artea be able to increase transactions / revenues with this campaign? By how much?

```{r df4, echo=TRUE}

#df_artea_5 <- df_artea %>%
#  filter(trans_after != 0) %>% 
 # group_by(test_coupon, channel_acq, shopping_cart) %>%
  #summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after), id_count = sum(counts(id))) %>% 
  #ggplot(aes(trans_after, fill = channel_acq)) +
  #geom_boxplot()
  #facet_wrap( ~ channel_acq, nrow = 1)
#df_artea_5

df_artea_6 <- df_artea %>%
  filter(trans_after != 0) %>% 
  group_by(test_coupon, channel_acq, shopping_cart) %>% 
  #summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after), id_count = sum(counts(id))) %>% 
  ggplot(aes(revenue_after, fill =as.character(test_coupon) )) +
  geom_histogram() + 
  facet_wrap( ~channel_acq , nrow = 1)

df_artea_7 <- df_artea %>%
  filter(trans_after != 0) %>% 
  group_by(test_coupon, channel_acq, shopping_cart) %>%
  mutate(num_past_purch_01 = ifelse(num_past_purch > 0, 1,0)) %>% 
  #summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after), id_count = sum(counts(id))) %>% 
  ggplot(aes(revenue_after, fill = channel_acq)) +
  geom_histogram() + 
  facet_wrap( ~ num_past_purch_01 + channel_acq, nrow = 2)


df_artea_8 <- df_artea %>%
  filter(trans_after != 0, test_coupon == 1) %>% 
  group_by( channel_acq) %>% 
  summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after), id_count = sum(counts(id)), revenue_avg = mean(revenue_after)) 


df_artea_9 <- df_artea %>% 
  filter( test_coupon == 1) %>% 
  group_by( channel_acq) %>% 
  summarise(revenue_after_tot = sum(revenue_after),trans_after_tot = sum(trans_after), id_count = sum(counts(id)), peso = trans_after_tot/id_count)


#Segments Test

#Create new variables
df_artea_improve = df_artea %>% 
  mutate(isOldCustomer = ifelse(num_past_purch>0,1,0),
         greatOldCustomer = ifelse(spent_last_purchase > 86,1,0))

#Group by every single variable, in this case we have two row for key(test coupon is could be 0 and 1)
df_artea_11 <- df_artea_improve %>%
  group_by(test_coupon, channel_acq, isOldCustomer, greatOldCustomer, shopping_cart, female, minority) %>% 
  summarise(revenue_after_tot = sum(revenue_after), trans_after_tot = sum(trans_after), id_count = sum(counts(id)), revenue_avg = mean(revenue_after)) %>% 
  arrange(channel_acq, isOldCustomer, greatOldCustomer, shopping_cart, female, minority,test_coupon, desc(revenue_avg))

#Aggregate the two of rows in one
df_artea_12 <- df_artea_11 %>% 
    group_by(channel_acq, isOldCustomer, greatOldCustomer, shopping_cart, female, minority) %>% 
  summarise(idCountTot = sum(id_count), sumRevenue =sum(revenue_after_tot), sumRevenueAVGTot = sum(revenue_avg)) %>% 
  mutate(potenzialIncome = sumRevenueAVGTot * idCountTot)
  
#Create the ID column
df_artea_12 <- rowid_to_column(df_artea_12, "ID")

#Add the char Segment to ID column
df_artea_12 <- df_artea_12 %>% 
  mutate(ID = paste("Segment ", ID))

#Sort the dataframe by the avarage revenue value
df_artea_12 <- df_artea_12 %>% 
  arrange(desc(sumRevenueAVGTot))


#Write the dataframe on CSV file
write.csv(df_artea_12,"Segments_Artea.csv", row.names = FALSE)

df_artea_12

```

```{r df5, echo=TRUE}
#model4
model4 <-lm(trans_after ~ channel_acq, data=df_artea)
msummary(model4)

#model5
model5 <-lm(trans_after ~  shopping_cart  , data=df_artea)
msummary(model5)

#model6
model6 <-lm(trans_after ~  shopping_cart + channel_acq , data=df_artea)
msummary(model6)

df_artea_new  <- df_artea %>% 
  select(trans_after, revenue_after, test_coupon, channel_acq, num_past_purch, spent_last_purchase, weeks_since_visit,shopping_cart) %>% 
  mutate(shopping_coupon = paste(shopping_cart,test_coupon,  sep = "" ))

modelNew <-glm(trans_after ~shopping_coupon, data=df_artea_new)
mosaic::msummary(modelNew)


modelNewL <-lm(trans_after ~ shopping_cart, shopping_coupon, data=df_artea_new)
mosaic::msummary(modelNewL)

```

## Analysis of created models

```{r modelAnalysis, echo= TRUE}

vif(model6)
check_model(model6)
huxreg(list("Model4" = model4, "Model6" = model6),
       statistics = c('Adj. R squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05,
       stars = NULL) %>% 
  set_caption('Comparison of models')

```
